Untitled probability judgment paper draft

### 2021-09-02 paper-rmd/ptn_platediagram.tex
added diag tex

\begin{tikzpicture}
      % Define nodes
      \node[obs]                               (y) {$y_{ijk}$};
      \node[det, above=of y] (mu) {$\mu_{ijk}$};
      \node[det, above=of mu, xshift=-1.2cm]  (d) {$d_j$};
      \node[det, above=of mu, xshift=1.2cm]  (d_prime) {$d_j'$};
      \node[latent, above=of d]  (delta) {$\delta_j$};
      \node[latent, above=of d_prime]  (delta_delta) {$\Delta\delta_j$};
      \node[latent, right=2cm of y]  (kappa) {$\kappa$};
      \node[latent, left=1cm of mu]            (p) {$\vec{p_{jk}}$};
      \node[latent, above=of delta, xshift=-.5cm]  (delta_pop) {$\overline{\delta}$};
      \node[latent, above=of delta_delta, xshift=-.5cm]  (delta_delta_pop) {$\overline{\Delta\delta}$};
      \node[latent, above=of delta, xshift=.5cm]  (sigma_delta) {$\sigma_{\delta}$};
      \node[latent, above=of delta_delta, xshift=.5cm]  (sigma_delta_delta) {$\sigma_{\Delta\delta}$};
      % Connect the nodes
      \edge {mu, kappa} {y} ; %
      \edge {d, d_prime} {mu}
      \edge {delta} {d, d_prime}
      \edge {delta_delta} {d_prime}
      \edge {p} {mu}
      \edge {delta_pop} {delta}
      \edge {delta_delta_pop} {delta_delta}
      \edge {sigma_delta} {delta}
      \edge {sigma_delta_delta} {delta_delta}

@@

>>>>

\begin{tikzpicture}

     % Define nodes
     \node[obs]                               (y) {$y_{ijk}$};
     \node[det, above=of y] (mu) {$\mu_{ijk}$};
     \node[det, above=of mu, xshift=-1.2cm]  (d) {$d_j$};
     \node[det, above=of mu, xshift=1.2cm]  (d_prime) {$d_j'$};
     \node[latent, above=of d]  (delta) {$\delta_j$};
     \node[latent, above=of d_prime]  (delta_delta) {$\Delta\delta_j$};
     \node[latent, right=2cm of y]  (kappa) {$\kappa$};
     \node[latent, left=1cm of mu]            (p) {$\vec{p_{jk}}$};

     % Connect the nodes
     \edge {mu, kappa} {y} ; %
     \edge {d, d_prime} {mu}
     \edge {delta} {d, d_prime}
     \edge {delta_delta} {d_prime}
     \edge {p} {mu}

@@

   %   \plate {} {(mu)(y)(p)(mup.north west)(mup.south west)} {$M$} ;
